Quantifying the home ground advantage

### 2022-07-08 inst/home_advantage.Rmd
nicer printing, do not echo messages
home advantage via hpyer3

@@

Here I analyse a small synthetic dataset for home ground advantage, then go on to discuss
a dataset presented by Agresti.

First load the package:
```{r,label=libload}
library(hyper2)
```

Now generate the dataset:

@@

>>>>

```{r,label=libload,echo=FALSE,print=FALSE,warning=FALSE,include=FALSE}
defaultW <- getOption("warn") 
options(warn = -1) 
library("hyper2",quietly=TRUE)
options(warn = defaultW)
```

@@

Here I analyse a small synthetic dataset for home ground advantage,
then go on to discuss a dataset presented by Agresti.  First generate
the dataset by hand:

@@

# hyper3 idiom

We may apply `hyper3` idiom to the dataset.  First we show
`home_away3()` being used with a specific value for $\lambda$:

```{r, label=hyper3_homeaway,cache=TRUE}
(o <- home_games_won + 1i*away_games_won)
f <- function(l){ maxp(home_away3(o,l),give=TRUE,n=1)$likes}
l <- exp(seq(from=log(2),to=log(6),len=10))
L <- sapply(l,f)
L <- L - max(L)
```

```{r,label=plothyper3home}
plot(l,L,type="b")
abline(h=c(0,-2))
plot(log(l),L,type="b")
abline(h=c(0,-2))
```

```{r, label=hyper3_baseball,cache=TRUE}
baseball_table
f <- function(l){ maxp(home_away3(baseball_table,l),give=TRUE,n=1)$likes}
l <- exp(seq(from=log(0.8),to=log(1.9),len=14))
L <- sapply(l,f)
L <- L - max(L)
```

```{r,label=plothyper3baseball}
plot(log(l),L,type="b")
abline(h=c(0,-2))
abline(v=0)
```

Now a formal test:

```{r,label=optimizebasebasll,cache=TRUE}
o <- optimize(f,c(0.2,0.4),maximum=TRUE)
o
```

```{r}
f(o$maximum) - f(0)
```
